---
title: ".hi[DS 498-02]"
subtitle: ".b[R Practice 2]"
author: ".b[Prof. Santetti] <br> Spring 2026"
output:
  xaringan::moon_reader:
    css: ['default', 'metropolis', 'metropolis-fonts', 'a-css.css']
    # self_contained: true
    nature:
      ratio: '8.5:11'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
layout: true
class: clear
---

<br><br><br><br><br>

.hi[.mono[INSTRUCTIONS]]: `R Practices` have the purpose of making students comfortable with the basics of  $\textsf{R}$ and $\textsf{R}$Studio for empirical economic analysis.

In this practice, you will improve your **intuition** about the main `{tidyverse}` functions: `select()`, `filter()`, `mutate()`, and `group_by()`. Not only is it important to know how to apply them in your own tasks, but also to **interpret** what a *pipeline* is doing when you are manipulating your data.



<br><br><br>


.right[.hi[Have fun!]]


---
class: clear


## Problem 1


Suppose you are working with an .mono[R] object called `price_data` in your .mono[R]Studio environment. (This file does not exist in reality.) It looks like the following:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

price_data <- tibble(
  year = c(2006, 2007, 2008, 2015, 2006, 2008, 2008, 2007, 2015),
  price = c(2.50, 3.00, 3.15, 2.00, 1.15, 2.75, 4.00, 5.15, 2.00),
  state = c("NY", "LA", "CA", "ID", "VT", "NY", "CT", "CT", "NY")
)

```


```{r}

price_data

```


For the following 5 parts, write down, in plain English, what each pipeline is trying to extract from this data set:

<br>

(a)

```{r, eval=FALSE}

price_data %>% 
  select(year, price)

```

(b)

```{r, eval=FALSE}

price_data %>% 
  filter(year > 2008)

```


(c)

```{r, eval=FALSE}

price_data_subset <- price_data %>% 
  filter(state %in% c("NY", "CT"))


```

(d)

```{r, eval=FALSE}

price_data %>% 
  mutate(price_cents = price * 100)

```

(e)

```{r, eval=FALSE}

price_data %>% 
  group_by(year) %>% 
  summarize(mean_price = mean(price))


```


---
exclude:true
