---
title: ".hi[DS 498-02]"
subtitle: ".b[R Practice 5]"
author: ".b[Prof. Santetti] <br> Spring 2026"
output:
  xaringan::moon_reader:
    css: ['default', 'metropolis', 'metropolis-fonts', 'a-css.css']
    # self_contained: true
    nature:
      ratio: '8.5:11'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
layout: true
class: clear
---

<br><br><br><br><br><br><br><br><br><br>

.hi[.mono[INSTRUCTIONS]]: `R Practices` have the purpose of making students comfortable with the basics of  $\textsf{R}$ and $\textsf{R}$Studio for empirical economic analysis.

In this practice, you will put to practice the necessary customization tasks to make your plots more informative to *any* audience.




<br><br><br>


.right[.hi[Have fun!]]


---
class: clear

## Problem 1

<br>

Check out the plots for parts (a) and (b). Working *backwards*, figure out the code that generated the two charts and replicate them. They come from the `brazilian_unemployment.csv` file that you can download from `theSpring`.

<br>

(a)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(scales)

br <- read_csv("brazilian_unemployment.csv")

```


```{r, echo=FALSE, warning=FALSE, message=FALSE, dev = "svg", fig.height = 3.5}

br %>% 
  ggplot(aes(x = period, y = unemp_rate)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Unemployment rate",
       title = "Unemployment rate (%), Brazil",
       subtitle = "1991–2021",
       caption = "Source: International Labour Organization.") +
  scale_y_continuous(labels = percent_format(scale = 1))
```


(b)

```{r, echo=FALSE, warning=FALSE, message=FALSE, dev = "svg", fig.height = 3.5}

br %>% 
  ggplot(aes(x = period, y = female_unemp_rate)) +
  geom_line() +
  geom_point() +
  labs(x = "Year", y = "Female unemployment rate",
       title = "Female unemployment rate (%), Brazil",
       subtitle = "1991–2021",
       caption = "Source: International Labour Organization.") +
  scale_y_continuous(labels = percent_format(scale = 1))
```


---
exclude:true
